\Title

### 2023-02-07 Grimaldi-etal-BiolCybernetics.tex
intro : c

The present paper proposes additional experiments on a recent model of spiking neurons with heterogeneous synaptic delays (i.e. time between the arrival of an afferent spike at a specific synapse and the contribution of the associated postsynaptic potential to the neuron's soma)~\cite{grimaldi_learning_2022}. This model was trained to solve a motion detection task on a synthetic event-based dataset. Once trained, its event-driven computations could be reduced drastically through the pruning of synapses, while maintaining top performance for classification. This showed that formal neurons can make use the precise timing of spikes to enhance neural computations. 
In the present paper, we extend the motion detection to a more ecological task. Instead of synthetic textures that were used to generate stimuli for which motion is controlled, we use natural images and random movements that mimic biological saccades. 
Through an ecological motion detection task, we study the emergence of spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task. First, we define the ecological cognitive task the model has to solve with the different datasets it will be tested on. Then, we develop a theoretically defined Heterogeneous Delays in Spiking Neural Network (HD-SNN) model capable of learning heterogenous synaptic delays. We will study the efficiency of the motion detection mechanism and in particular its resilience to synaptic weight pruning. This will allow us to show how such a model can provide an efficient solution to the energy/accuracy trade-off. 

>>>>

The present paper proposes additional experiments extending a recent model of spiking neurons with heterogeneous synaptic delays (i.e., the time between the arrival of an afferent spike at a given synapse and the contribution of the associated postsynaptic potential to the neuron's soma)~\cite{grimaldi_learning_2022}. This particular model was trained to solve a motion detection task on a synthetic event-based dataset generated by moving parameterized textures. Once trained, the volume of event-driven computations could be drastically reduced by pruning the synapses, while maintaining top performance for the classification task. This was a demonstration that formal neurons can exploit the precise timing of spikes to improve neural computation. 
In the present work, we extend motion detection to a more ecological task. Instead of the synthetic textures that have been used to generate motion-driven stimuli, we use natural images and random movements that mimic biological saccades. 
Using an ecological motion detection task, we study the emergence of spatio-temporal spiking motifs when a single layer of spiking neurons is trained on a supervised classification task. First, we define the ecological cognitive task the model has to solve with the different datasets it will be tested on. Then, we develop a theoretically defined Heterogeneous Delays in Spiking Neural Network (HD-SNN) model capable of learning heterogeneous synaptic delays. We will investigate the efficiency of the motion detection mechanism and in particular its resilience to synaptic weight pruning. In this way, we will be able to show how such a model can provide an efficient solution to the trade-off between energy and accuracy.
